one target

### 2018-08-24 E2/analysis/histsWithFitsOneTarget.Rmd
exclusions

AA<- twoTarget %>% filter(subject=="AA")
#Function for one subject, calculating how many stream conditions failed the test
calcExclude<- function(oneSub) {
  oneSub %>% group_by(stream,orientation)
}
#first, collapse over trials
#https://stackoverflow.com/questions/51978519/summarise-numeric-columns-return-last-value-of-non-numeric
tw<- twoTarget %>% group_by(subject,stream,orientation) %>% select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#for each subject, count pLRtest instances >.05 and efficay <.1
B<-tw %>% ungroup %>% group_by(subject) %>% summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))                                                              
#B %>% print(n=Inf)
exclude <- B %>% filter(LRtestFails>=3, effFails >

# efficacy is below 10% in both streams in either the upright or the reversed orientation.
# To calculate that, need to group by subject and orientation
C<-tw %>% ungroup %>% group_by(subject,orientation) %>% summarise(bothEffsFailed = sum(efficacy<.1)==2)
#Find which subjects, if any, has a bothEffsFailed==TRUE
lowEff<- C %>% filter(bothEffsFailed==TRUE)
lowEff <- unique(lowEff$subject)

>>>>

#first, collapse over trials
#https://stackoverflow.com/questions/51978519/summarise-numeric-columns-return-last-value-of-non-numeric
tw<- twoTarget %>% group_by(subject,stream,orientation) %>% select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#for each subject, count pLRtest instances >.05 and efficay <.1
B<-tw %>% ungroup %>% group_by(subject) %>% summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))                                                              
#B %>% print(n=Inf)
LRtestLosers <- B %>% filter(LRtestFails>=3)
LRtestLosers<- unique(LRtestLosers$subject)
# efficacy is below 10% in both streams in either the upright or the reversed orientation.
# To calculate that, need to group by subject and orientation
C<-tw %>% ungroup %>% group_by(subject,orientation) %>% summarise(bothEffsFailed = sum(efficacy<.1)==2)
#Find which subjects, if any, has a bothEffsFailed==TRUE
lowEff<- C %>% filter(bothEffsFailed==TRUE)
lowEffs <- unique(lowEff$subject)
```

I suppose there are 4 one-target conditions also, upright/reversed x left/right
```{r }
#Calculate exclusions based on one-target performance
#oneTarget<- dg %>% filter(targetSide!="Both")
one<- oneTarget %>% group_by(subject,targetSide,orientation) %>% 
  select(-targetStreamOrientations,-letterSeq) %>% #can't include list columns
  select(-trial,-targetSP,-respSP,-respOrder) %>% #clear detritus so easier to see
  summarise_all( function(x){ if(is.numeric(x)){ return(mean(x)) } else{ nth(x,-1) } })

#Should probably look at the difference in efficacy between the left and the right
one %>% group_by(subject,targetSide) %>%   function(x) { x$effDiff = x %>% filter(stream=="Left")   -    x %>% filter(stream=="Right") }

one %>% group_by(subject,targetSide) %>% summarise_at("efficacy",
       function(x) { x %>% filter(stream=="Left")   -    x %>% filter(stream=="Right") }  )

  mutate(effDiff = 
       function(x) { x %>% filter(stream=="Left")$efficacy   -    x %>% filter(stream=="Right")$efficacy }  )

  summarise(LRtestFails = sum(pLRtest>.05), effFails = sum(efficacy<.1))

Make master list of Ss to exclude also from one-target condition??

Actually exclude the losers
```{r exclude, echo=FALSE}

afterExclusions<- tw %>% filter(  !(subject %in% lowEffs)   )
